Roster Review (Generic)

### 2019-06-04 rosterReview_generic.Rmd
Latest projections, further fleshing out per-position view

ggplotly(team_pos)
```

>>>>

ggplotly(team_pos)

rosters_by_position %>% 
  filter(!is.na(manager)) %>% 
  group_by(position) %>% 
  count() %>% 
  ungroup() -> count_by_pos

rosters_by_position %>% 
  group_by(position) %>% 
  arrange(zar %>% desc()) %>% 
  mutate(num = row_number()) %>% 
  ungroup %>% 
  full_join(count_by_pos, "position") %>% 
  filter(num <= 1.5 * n) %>% 
  select(team, manager, name_full, position, zar) %>% View()
```
